A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2015-01-27 ms.tex
Explain interferometer sensitivity to uniform sky
from 139fc7b:
============

In ms.tex,

(*) Add paragraph in S7.1 to explain wide-field interferometers are
sensitive to a uniformly sky

>>>>

Na\"{i}vely, only single element antennas are sensitive to a uniform brightness distribution while interferometers are not. However, an examination of equation~\ref{eqn:obsvis} shows it resembles a Fourier transform when the sky brightness is expressed in a coordinate system of direction cosines \citep{tay99,tho01}. In such a framework, the solid angle subtended by a unit interval in direction cosine increases as the secant of the angle away from zenith, which is significant in wide--field measurements. A uniformly illuminated sky does not appear so in this frame. Therefore, a uniformly illuminated sky will excite wide--field interferometers.
